Articles of Association of London Hackspace Ltd.

### 2011-07-26 constitution/articles-body.tex
Add Minutes section

>>>>

\section{Minutes}

\item
The directors must keep minutes of all:
    \begin{enumerate}
        \item
            appointments of officers made by the directors;
        \item
            proceedings at meetings of the charity;
        \item
            meetings of the directors and committees of directors including:
            \begin{enumerate}
                \item
                    the names of the directors present at the meeting;
                \item
                    the decisions made at the meetings; and
                \item
                    where appropriate the reasons for the decisions.
            \end{enumerate}
    \end{enumerate}
